Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-05-02 paper.tex
two sentences about what brunn does

\author{Charles A Darwin\correspondingauthor$^{1,2}$%
       \email{Charles A Darwin\correspondingauthor - charles@londonzoo.co.uk}%
      \and 
         Egon L Willighagen$^3$%
         \email{Egon L Willighagen - egon.willighagen@ki.se}
     \and 
         Rajarshi Guha$^4$%
         \email{Rajarshi Guha - guhar@mail.nih.gov}
	 \and 
	     Christoph Steinbeck$^6$%
	         \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
     \and 
         Noel M O'Boyle$^5$%
         \email{Noel M O'Boyle - n.oboyle@ucc.ie}
     \and 
         Ola Spjuth$^9$%
         \email{Noel M O'Boyle - n.oboyle@ucc.ie}
     \and 
         Jonathan Alvarsson$^9$%
         \email{Jonathan Alvarsson - jonathan.alvarsson@farmbio.uu.se}
     \and 
         Peter Murray-Rust$^7$%
         \email{Peter Murray-Rust - pm286@cam.ac.uk}
     \and 
         Daniel M Lowe$^7$%
         \email{Daniel Lowe - dl387@cam.ac.uk}
     \and
         Robert Hanson$^8$%
         \email{Robert Hanson - hansonr@stolaf.edu}
      \and
         Dmitry Pavlov$^8$%
         \email{Dmitry Pavlov - dpavlov@ggasoftware.com}
      \and
         Igor V Filippov\correspondingauthor$^{10}$%
         \email{Igor V Filippov\correspondingauthor - igorf@helix.nih.gov}
      \and
         Jane E Doe\correspondingauthor$^2$%
         \email{Jane E Doe\correspondingauthor - jane.e.doe@cambridge.co.uk}
      }

@@

\address{%
    \iid(1)Life Sciences Department, Kings College London, Cornwall House,%
        Waterloo Road, London, UK\\
    \iid(2)Department of Zoology, Cambridge, Waterloo Road, London, UK\\
    \iid(3)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden\\
    \iid(5)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland\\
    \iid(6)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK\\
    \iid(7)Unilever Centre for Molecular Science Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK\\
    \iid(8)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia\\
    \iid(9)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(10)NIH, Somewhere in the US, USA
}%

@@

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such software, based
on the CDK and Open Babel, respectively. Bioclipse is an award-winning
molecular workbench for life sciences with a dynamic plugin architecture, and
which wraps cheminformatics functionality behind user-friendly interfaces and
graphical editors. All functionality in Bioclipse is completely scriptable
using an integrated high-level language called Bioclipse Scripting Language
(BSL), which can be used for scripted research or to automate complex
tasks~\cite{Bioclipse2}. Bioclipse in turn acts as base for other software
such as Brunn~\cite{Brunn}, which is a laboratory information system for
microplate based high-throughput screening. In this manner open source projects
empower other open source projects.

>>>>

\author{Charles A Darwin\correspondingauthor$^{1,2}$%
       \email{Charles A Darwin\correspondingauthor - charles@londonzoo.co.uk}%
      \and 
         Egon L Willighagen$^3$%
         \email{Egon L Willighagen - egon.willighagen@ki.se}
     \and 
         Rajarshi Guha$^4$%
         \email{Rajarshi Guha - guhar@mail.nih.gov}
	 \and 
	     Christoph Steinbeck$^6$%
	         \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
     \and 
         Noel M O'Boyle$^5$%
         \email{Noel M O'Boyle - n.oboyle@ucc.ie}
     \and
         Geoffrey R Hutchison$^6$%
         \email{Geoffrey R Hutchison - geoffh@pitt.edu}
     \and 
         Ola Spjuth$^9$%
         \email{ola.spjuth@farmbio.uu.se}
     \and 
         Jonathan Alvarsson$^9$%
         \email{Jonathan Alvarsson - jonathan.alvarsson@farmbio.uu.se}
     \and 
         Peter Murray-Rust$^7$%
         \email{Peter Murray-Rust - pm286@cam.ac.uk}
     \and 
         Daniel M Lowe$^7$%
         \email{Daniel Lowe - dl387@cam.ac.uk}
     \and
         Robert Hanson$^8$%
         \email{Robert Hanson - hansonr@stolaf.edu}
      \and
         Dmitry Pavlov$^8$%
         \email{Dmitry Pavlov - dpavlov@ggasoftware.com}
      \and
         Igor V Filippov\correspondingauthor$^{10}$%
         \email{Igor V Filippov\correspondingauthor - igorf@helix.nih.gov}
     \and
         Jane E Doe\correspondingauthor$^2$%
         \email{Jane E Doe\correspondingauthor - jane.e.doe@cambridge.co.uk}
      }

@@

\address{%
    \iid(1)Life Sciences Department, Kings College London, Cornwall House,%
        Waterloo Road, London, UK\\
    \iid(2)Department of Zoology, Cambridge, Waterloo Road, London, UK\\
    \iid(3)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden\\
    \iid(5)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland\\
    \iid(6)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK\\
    \iid(7)Unilever Centre for Molecular Science Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK\\
    \iid(8)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia\\
    \iid(9)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(10)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA\\
    \iid(11)NIH, Somewhere in the US, USA
}%

@@

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such software, based
on the CDK and Open Babel, respectively. Bioclipse is an award-winning
molecular workbench for life sciences with a dynamic plugin architecture, and
which wraps cheminformatics functionality behind user-friendly interfaces and
graphical editors. All functionality in Bioclipse is completely scriptable
using an integrated high-level language called Bioclipse Scripting Language
(BSL), which can be used for scripted research or to automate complex
tasks~\cite{Bioclipse2}. Bioclipse in turn acts as base for other software
such as Brunn~\cite{Brunn}, which is a laboratory information system for
microplate based high-throughput screening. Brunn provides a grahical interface
for handling different plate layouts and dilution series. It can automaticly
generate dose response curves and calculate IC$_{50}$-values. In this manner
open source projects empower other open source projects.
